### 2022-12-07 output/01_exploratory/tables/total_val_results_table.tex
Created estimation tables

{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabular}{l*{4}{c}}
\toprule
                    &\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}\\
\midrule
judgment\_for\_plaintiff&   3259178.0\sym{***}&   1507062.7\sym{**} &   1507062.7\sym{**} &    751962.4         \\
                    &      (4.27)         &      (2.61)         &      (2.61)         &      (0.26)         \\
\addlinespace
file\_year=2019      &                     &           0         &           0         &                     \\
                    &                     &         (.)         &         (.)         &                     \\
\addlinespace
file\_year=2020      &                     &   -129326.5         &   -129326.5         &                     \\
                    &                     &     (-0.22)         &     (-0.22)         &                     \\
\addlinespace
file\_year=2021      &                     &   2343272.8         &   2343272.8         &                     \\
                    &                     &      (1.01)         &      (1.01)         &                     \\
\addlinespace
Abington            &                     &           0         &           0         &                     \\
                    &                     &         (.)         &         (.)         &                     \\
\addlinespace
Acton               &                     &  -8845941.7         &  -8845941.7         &                     \\
                    &                     &     (-1.10)         &     (-1.10)         &                     \\
\addlinespace
Adams               &                     & -26295427.0\sym{***}& -26295427.0\sym{***}&                     \\
                    &                     &     (-5.72)         &     (-5.72)         &                     \\
\addlinespace
Agawam              &                     & -22781989.3\sym{***}& -22781989.3\sym{***}&                     \\
                    &                     &     (-3.77)         &     (-3.77)         &                     \\
\addlinespace
Amesbury            &                     & -22667125.4\sym{**} & -22667125.4\sym{**} &                     \\
                    &                     &     (-2.82)         &     (-2.82)         &                     \\
\addlinespace
Amherst             &                     & -13994734.3\sym{*}  & -13994734.3\sym{*}  &                     \\
                    &                     &     (-2.40)         &     (-2.40)         &                     \\
\addlinespace
Andover             &                     &   -749699.0         &   -749699.0         &                     \\
                    &                     &     (-0.17)         &     (-0.17)         &                     \\
\addlinespace
Athol               &                     & -26350442.5\sym{***}& -26350442.5\sym{***}&                     \\
                    &                     &     (-3.99)         &     (-3.99)         &                     \\
\addlinespace
Attleboro           &                     & -24327184.2\sym{***}& -24327184.2\sym{***}&                     \\
                    &                     &     (-5.29)         &     (-5.29)         &                     \\
\addlinespace
Auburn              &                     & -26064121.1\sym{***}& -26064121.1\sym{***}&                     \\
                    &                     &     (-3.50)         &     (-3.50)         &                     \\
\addlinespace
Bedford             &                     &   5756678.9         &   5756678.9         &                     \\
                    &                     &      (0.77)         &      (0.77)         &                     \\
\addlinespace
Belchertown         &                     & -25142479.5\sym{***}& -25142479.5\sym{***}&                     \\
                    &                     &     (-5.23)         &     (-5.23)         &                     \\
\addlinespace
Bellingham          &                     &  18531792.0\sym{*}  &  18531792.0\sym{*}  &                     \\
                    &                     &      (2.49)         &      (2.49)         &                     \\
\addlinespace
Beverly             &                     & -15591295.2\sym{***}& -15591295.2\sym{***}&                     \\
                    &                     &     (-4.23)         &     (-4.23)         &                     \\
\addlinespace
Billerica           &                     &   9390507.4\sym{*}  &   9390507.4\sym{*}  &                     \\
                    &                     &      (2.07)         &      (2.07)         &                     \\
\addlinespace
Braintree           &                     &  35327975.2\sym{***}&  35327975.2\sym{***}&                     \\
                    &                     &      (7.88)         &      (7.88)         &                     \\
\addlinespace
Brewster            &                     & -25347499.3\sym{**} & -25347499.3\sym{**} &                     \\
                    &                     &     (-3.15)         &     (-3.15)         &                     \\
\addlinespace
Bridgewater         &                     &  11554226.6\sym{**} &  11554226.6\sym{**} &                     \\
                    &                     &      (2.85)         &      (2.85)         &                     \\
\addlinespace
Brockton            &                     & -21848926.9\sym{***}& -21848926.9\sym{***}&                     \\
                    &                     &     (-7.20)         &     (-7.20)         &                     \\
\addlinespace
Brookline           &                     & -14165718.5         & -14165718.5         &                     \\
                    &                     &     (-1.90)         &     (-1.90)         &                     \\
\addlinespace
Cambridge           &                     &  42468310.1\sym{***}&  42468310.1\sym{***}&                     \\
                    &                     &      (9.10)         &      (9.10)         &                     \\
\addlinespace
Canton              &                     &   5921639.1         &   5921639.1         &                     \\
                    &                     &      (1.34)         &      (1.34)         &                     \\
\addlinespace
Chelmsford          &                     &  -3878300.3         &  -3878300.3         &                     \\
                    &                     &     (-0.48)         &     (-0.48)         &                     \\
\addlinespace
Chelsea             &                     &  -6087119.2         &  -6087119.2         &                     \\
                    &                     &     (-1.11)         &     (-1.11)         &                     \\
\addlinespace
Chicopee            &                     & -23100145.0\sym{***}& -23100145.0\sym{***}&                     \\
                    &                     &     (-6.57)         &     (-6.57)         &                     \\
\addlinespace
Clinton             &                     & -25980685.6\sym{***}& -25980685.6\sym{***}&                     \\
                    &                     &     (-4.30)         &     (-4.30)         &                     \\
\addlinespace
Concord             &                     &  36262535.7\sym{***}&  36262535.7\sym{***}&                     \\
                    &                     &      (4.88)         &      (4.88)         &                     \\
\addlinespace
Danvers             &                     &   -350734.0         &   -350734.0         &                     \\
                    &                     &     (-0.06)         &     (-0.06)         &                     \\
\addlinespace
Dracut              &                     & -23566660.9\sym{***}& -23566660.9\sym{***}&                     \\
                    &                     &     (-4.30)         &     (-4.30)         &                     \\
\addlinespace
Dudley              &                     & -26862280.4\sym{***}& -26862280.4\sym{***}&                     \\
                    &                     &     (-3.85)         &     (-3.85)         &                     \\
\addlinespace
Duxbury             &                     & -16553871.4\sym{*}  & -16553871.4\sym{*}  &                     \\
                    &                     &     (-2.37)         &     (-2.37)         &                     \\
\addlinespace
East Wareham        &                     & -18675454.5\sym{*}  & -18675454.5\sym{*}  &                     \\
                    &                     &     (-2.51)         &     (-2.51)         &                     \\
\addlinespace
Everett             &                     &  -8839883.1         &  -8839883.1         &                     \\
                    &                     &     (-1.89)         &     (-1.89)         &                     \\
\addlinespace
Fairhaven           &                     & -25898741.3\sym{***}& -25898741.3\sym{***}&                     \\
                    &                     &     (-5.48)         &     (-5.48)         &                     \\
\addlinespace
Fall River          &                     & -21875817.7\sym{***}& -21875817.7\sym{***}&                     \\
                    &                     &     (-6.91)         &     (-6.91)         &                     \\
\addlinespace
Feeding Hills       &                     & -22823447.4\sym{***}& -22823447.4\sym{***}&                     \\
                    &                     &     (-5.03)         &     (-5.03)         &                     \\
\addlinespace
Fitchburg           &                     & -25581554.5\sym{***}& -25581554.5\sym{***}&                     \\
                    &                     &     (-7.97)         &     (-7.97)         &                     \\
\addlinespace
Foxboro             &                     &  22618498.2\sym{***}&  22618498.2\sym{***}&                     \\
                    &                     &      (3.74)         &      (3.74)         &                     \\
\addlinespace
Foxborough          &                     &  21596274.6\sym{**} &  21596274.6\sym{**} &                     \\
                    &                     &      (2.68)         &      (2.68)         &                     \\
\addlinespace
Framingham          &                     &  -4392422.6         &  -4392422.6         &                     \\
                    &                     &     (-1.26)         &     (-1.26)         &                     \\
\addlinespace
Franklin            &                     &  -3437183.4         &  -3437183.4         &                     \\
                    &                     &     (-0.72)         &     (-0.72)         &                     \\
\addlinespace
Gardner             &                     & -22989976.9\sym{***}& -22989976.9\sym{***}&                     \\
                    &                     &     (-5.12)         &     (-5.12)         &                     \\
\addlinespace
Gloucester          &                     & -18804855.2\sym{***}& -18804855.2\sym{***}&                     \\
                    &                     &     (-4.80)         &     (-4.80)         &                     \\
\addlinespace
Grafton             &                     & -16016646.8\sym{*}  & -16016646.8\sym{*}  &                     \\
                    &                     &     (-1.99)         &     (-1.99)         &                     \\
\addlinespace
Greenfield          &                     & -23459956.9\sym{***}& -23459956.9\sym{***}&                     \\
                    &                     &     (-4.69)         &     (-4.69)         &                     \\
\addlinespace
Hanson              &                     & -26499939.3\sym{***}& -26499939.3\sym{***}&                     \\
                    &                     &     (-3.29)         &     (-3.29)         &                     \\
\addlinespace
Haverhill           &                     & -20800293.3\sym{***}& -20800293.3\sym{***}&                     \\
                    &                     &     (-5.77)         &     (-5.77)         &                     \\
\addlinespace
Holyoke             &                     & -24189959.6\sym{***}& -24189959.6\sym{***}&                     \\
                    &                     &     (-6.70)         &     (-6.70)         &                     \\
\addlinespace
Hudson              &                     & -26242808.0\sym{***}& -26242808.0\sym{***}&                     \\
                    &                     &     (-3.53)         &     (-3.53)         &                     \\
\addlinespace
Hull                &                     & -17550050.6\sym{***}& -17550050.6\sym{***}&                     \\
                    &                     &     (-3.52)         &     (-3.52)         &                     \\
\addlinespace
Hyannis             &                     & -23763038.9\sym{***}& -23763038.9\sym{***}&                     \\
                    &                     &     (-4.08)         &     (-4.08)         &                     \\
\addlinespace
Indian Orchard      &                     & -25842404.0\sym{***}& -25842404.0\sym{***}&                     \\
                    &                     &     (-6.83)         &     (-6.83)         &                     \\
\addlinespace
Ipswich             &                     & -23775846.2\sym{***}& -23775846.2\sym{***}&                     \\
                    &                     &     (-3.77)         &     (-3.77)         &                     \\
\addlinespace
Lakeville           &                     & -21406455.4\sym{***}& -21406455.4\sym{***}&                     \\
                    &                     &     (-3.80)         &     (-3.80)         &                     \\
\addlinespace
Lawrence            &                     & -23418520.4\sym{***}& -23418520.4\sym{***}&                     \\
                    &                     &     (-7.75)         &     (-7.75)         &                     \\
\addlinespace
Leominster          &                     & -21878759.1\sym{***}& -21878759.1\sym{***}&                     \\
                    &                     &     (-5.85)         &     (-5.85)         &                     \\
\addlinespace
Lowell              &                     & -19476530.9\sym{***}& -19476530.9\sym{***}&                     \\
                    &                     &     (-6.51)         &     (-6.51)         &                     \\
\addlinespace
Ludlow              &                     & -25548082.3\sym{***}& -25548082.3\sym{***}&                     \\
                    &                     &     (-5.02)         &     (-5.02)         &                     \\
\addlinespace
Lunenburg           &                     & -26707931.8\sym{***}& -26707931.8\sym{***}&                     \\
                    &                     &     (-3.32)         &     (-3.32)         &                     \\
\addlinespace
Lynn                &                     & -21462921.1\sym{***}& -21462921.1\sym{***}&                     \\
                    &                     &     (-6.33)         &     (-6.33)         &                     \\
\addlinespace
Lynnfield           &                     &    429208.2         &    429208.2         &                     \\
                    &                     &      (0.05)         &      (0.05)         &                     \\
\addlinespace
Malden              &                     &   6937988.9         &   6937988.9         &                     \\
                    &                     &      (1.94)         &      (1.94)         &                     \\
\addlinespace
Mansfield           &                     & -15826011.6\sym{**} & -15826011.6\sym{**} &                     \\
                    &                     &     (-3.17)         &     (-3.17)         &                     \\
\addlinespace
Marblehead          &                     & -24872624.7\sym{***}& -24872624.7\sym{***}&                     \\
                    &                     &     (-4.12)         &     (-4.12)         &                     \\
\addlinespace
Marshfield          &                     & -25486617.7\sym{***}& -25486617.7\sym{***}&                     \\
                    &                     &     (-5.59)         &     (-5.59)         &                     \\
\addlinespace
Mashpee             &                     & -24274364.9\sym{**} & -24274364.9\sym{**} &                     \\
                    &                     &     (-3.26)         &     (-3.26)         &                     \\
\addlinespace
Methuen             &                     & -17599579.2\sym{***}& -17599579.2\sym{***}&                     \\
                    &                     &     (-5.10)         &     (-5.10)         &                     \\
\addlinespace
Middleboro          &                     & -15039148.7\sym{***}& -15039148.7\sym{***}&                     \\
                    &                     &     (-3.79)         &     (-3.79)         &                     \\
\addlinespace
Milford             &                     &  -7530303.0         &  -7530303.0         &                     \\
                    &                     &     (-1.54)         &     (-1.54)         &                     \\
\addlinespace
Millbury            &                     & -23455764.3\sym{***}& -23455764.3\sym{***}&                     \\
                    &                     &     (-3.55)         &     (-3.55)         &                     \\
\addlinespace
Needham             &                     &  45061315.4\sym{***}&  45061315.4\sym{***}&                     \\
                    &                     &      (8.23)         &      (8.23)         &                     \\
\addlinespace
New Bedford         &                     & -25410999.4\sym{***}& -25410999.4\sym{***}&                     \\
                    &                     &     (-8.35)         &     (-8.35)         &                     \\
\addlinespace
Newburyport         &                     & -21570253.8\sym{***}& -21570253.8\sym{***}&                     \\
                    &                     &     (-4.14)         &     (-4.14)         &                     \\
\addlinespace
North Adams         &                     & -24978653.4\sym{***}& -24978653.4\sym{***}&                     \\
                    &                     &     (-5.11)         &     (-5.11)         &                     \\
\addlinespace
North Andover       &                     &  -4813790.9         &  -4813790.9         &                     \\
                    &                     &     (-1.16)         &     (-1.16)         &                     \\
\addlinespace
North Attleboro     &                     & -24642950.8\sym{***}& -24642950.8\sym{***}&                     \\
                    &                     &     (-5.21)         &     (-5.21)         &                     \\
\addlinespace
North Billerica     &                     &  -9778512.3         &  -9778512.3         &                     \\
                    &                     &     (-1.62)         &     (-1.62)         &                     \\
\addlinespace
North Dartmouth     &                     & -15474811.8         & -15474811.8         &                     \\
                    &                     &     (-1.92)         &     (-1.92)         &                     \\
\addlinespace
Northampton         &                     & -25051692.1\sym{***}& -25051692.1\sym{***}&                     \\
                    &                     &     (-4.31)         &     (-4.31)         &                     \\
\addlinespace
Northborough        &                     &  49673648.2\sym{***}&  49673648.2\sym{***}&                     \\
                    &                     &      (8.22)         &      (8.22)         &                     \\
\addlinespace
Norton              &                     &  -7666259.5         &  -7666259.5         &                     \\
                    &                     &     (-1.40)         &     (-1.40)         &                     \\
\addlinespace
Norwood             &                     & 135282132.6\sym{***}& 135282132.6\sym{***}&                     \\
                    &                     &     (32.98)         &     (32.98)         &                     \\
\addlinespace
Oxford              &                     & -12619694.0         & -12619694.0         &                     \\
                    &                     &     (-1.91)         &     (-1.91)         &                     \\
\addlinespace
Peabody             &                     &   9977389.1\sym{**} &   9977389.1\sym{**} &                     \\
                    &                     &      (2.94)         &      (2.94)         &                     \\
\addlinespace
Pittsfield          &                     & -25617594.5\sym{***}& -25617594.5\sym{***}&                     \\
                    &                     &     (-7.64)         &     (-7.64)         &                     \\
\addlinespace
Plymouth            &                     & -26008178.7\sym{***}& -26008178.7\sym{***}&                     \\
                    &                     &     (-4.57)         &     (-4.57)         &                     \\
\addlinespace
Quincy              &                     &  -5122621.6         &  -5122621.6         &                     \\
                    &                     &     (-1.03)         &     (-1.03)         &                     \\
\addlinespace
Randolph            &                     &  -2407969.7         &  -2407969.7         &                     \\
                    &                     &     (-0.67)         &     (-0.67)         &                     \\
\addlinespace
Revere              &                     &   3580359.7         &   3580359.7         &                     \\
                    &                     &      (0.45)         &      (0.45)         &                     \\
\addlinespace
Rockland            &                     & -20926211.3\sym{***}& -20926211.3\sym{***}&                     \\
                    &                     &     (-5.36)         &     (-5.36)         &                     \\
\addlinespace
Salem               &                     & -19892879.6\sym{***}& -19892879.6\sym{***}&                     \\
                    &                     &     (-5.38)         &     (-5.38)         &                     \\
\addlinespace
Sandwich            &                     & -25081254.5\sym{***}& -25081254.5\sym{***}&                     \\
                    &                     &     (-3.37)         &     (-3.37)         &                     \\
\addlinespace
Saugus              &                     &   -340993.8         &   -340993.8         &                     \\
                    &                     &     (-0.08)         &     (-0.08)         &                     \\
\addlinespace
Seekonk             &                     &  12790285.1\sym{**} &  12790285.1\sym{**} &                     \\
                    &                     &      (2.78)         &      (2.78)         &                     \\
\addlinespace
Shirley             &                     & -26310641.7\sym{***}& -26310641.7\sym{***}&                     \\
                    &                     &     (-4.67)         &     (-4.67)         &                     \\
\addlinespace
Shrewsbury          &                     & -13932047.6\sym{*}  & -13932047.6\sym{*}  &                     \\
                    &                     &     (-2.21)         &     (-2.21)         &                     \\
\addlinespace
Somerville          &                     & -23932481.5\sym{***}& -23932481.5\sym{***}&                     \\
                    &                     &     (-3.63)         &     (-3.63)         &                     \\
\addlinespace
South Hadley        &                     & -24837142.8\sym{***}& -24837142.8\sym{***}&                     \\
                    &                     &     (-4.77)         &     (-4.77)         &                     \\
\addlinespace
Southbridge         &                     & -25986587.2\sym{***}& -25986587.2\sym{***}&                     \\
                    &                     &     (-6.88)         &     (-6.88)         &                     \\
\addlinespace
Southwick           &                     & -25424600.0\sym{***}& -25424600.0\sym{***}&                     \\
                    &                     &     (-3.65)         &     (-3.65)         &                     \\
\addlinespace
Spencer             &                     & -26098696.3\sym{***}& -26098696.3\sym{***}&                     \\
                    &                     &     (-5.12)         &     (-5.12)         &                     \\
\addlinespace
Springfield         &                     & -21965898.8\sym{***}& -21965898.8\sym{***}&                     \\
                    &                     &     (-7.48)         &     (-7.48)         &                     \\
\addlinespace
Stoughton           &                     & -13918342.5\sym{***}& -13918342.5\sym{***}&                     \\
                    &                     &     (-3.68)         &     (-3.68)         &                     \\
\addlinespace
Swampscott          &                     &  -6303624.1         &  -6303624.1         &                     \\
                    &                     &     (-1.18)         &     (-1.18)         &                     \\
\addlinespace
Taunton             &                     & -25117756.6\sym{***}& -25117756.6\sym{***}&                     \\
                    &                     &     (-7.25)         &     (-7.25)         &                     \\
\addlinespace
Tewksbury           &                     &   4960284.1         &   4960284.1         &                     \\
                    &                     &      (1.11)         &      (1.11)         &                     \\
\addlinespace
Three Rivers        &                     & -25876069.9\sym{***}& -25876069.9\sym{***}&                     \\
                    &                     &     (-3.71)         &     (-3.71)         &                     \\
\addlinespace
Tyngsboro           &                     & -23326009.0\sym{***}& -23326009.0\sym{***}&                     \\
                    &                     &     (-3.35)         &     (-3.35)         &                     \\
\addlinespace
Wakefield           &                     & -13733066.0\sym{**} & -13733066.0\sym{**} &                     \\
                    &                     &     (-2.70)         &     (-2.70)         &                     \\
\addlinespace
Walpole             &                     & -13399797.3\sym{*}  & -13399797.3\sym{*}  &                     \\
                    &                     &     (-2.30)         &     (-2.30)         &                     \\
\addlinespace
Waltham             &                     &    435329.0         &    435329.0         &                     \\
                    &                     &      (0.12)         &      (0.12)         &                     \\
\addlinespace
Ware                &                     & -26606046.0\sym{***}& -26606046.0\sym{***}&                     \\
                    &                     &     (-5.72)         &     (-5.72)         &                     \\
\addlinespace
Watertown           &                     &  22686557.5\sym{***}&  22686557.5\sym{***}&                     \\
                    &                     &      (3.44)         &      (3.44)         &                     \\
\addlinespace
Webster             &                     & -25363678.1\sym{***}& -25363678.1\sym{***}&                     \\
                    &                     &     (-4.03)         &     (-4.03)         &                     \\
\addlinespace
West Springfield    &                     & -25265471.7\sym{***}& -25265471.7\sym{***}&                     \\
                    &                     &     (-5.88)         &     (-5.88)         &                     \\
\addlinespace
Westborough         &                     &   5644711.5         &   5644711.5         &                     \\
                    &                     &      (1.29)         &      (1.29)         &                     \\
\addlinespace
Westwood            &                     &   5943592.0         &   5943592.0         &                     \\
                    &                     &      (0.80)         &      (0.80)         &                     \\
\addlinespace
Weymouth            &                     &  -2354873.6         &  -2354873.6         &                     \\
                    &                     &     (-0.44)         &     (-0.44)         &                     \\
\addlinespace
Whitinsville        &                     & -26113031.8\sym{**} & -26113031.8\sym{**} &                     \\
                    &                     &     (-3.25)         &     (-3.25)         &                     \\
\addlinespace
Whitman             &                     & -24430447.6\sym{***}& -24430447.6\sym{***}&                     \\
                    &                     &     (-4.69)         &     (-4.69)         &                     \\
\addlinespace
Winchendon          &                     & -26829580.4\sym{***}& -26829580.4\sym{***}&                     \\
                    &                     &     (-3.85)         &     (-3.85)         &                     \\
\addlinespace
Woburn              &                     &  51069929.9\sym{***}&  51069929.9\sym{***}&                     \\
                    &                     &      (9.05)         &      (9.05)         &                     \\
\addlinespace
Worcester           &                     & -23487792.3\sym{***}& -23487792.3\sym{***}&                     \\
                    &                     &     (-7.79)         &     (-7.79)         &                     \\
\addlinespace
group(property\_address\_city file\_year)=1&                     &                     &                     &           0         \\
                    &                     &                     &                     &         (.)         \\
\addlinespace
group(property\_address\_city file\_year)=2&                     &                     &                     & -25607702.2\sym{**} \\
                    &                     &                     &                     &     (-2.99)         \\
\addlinespace
group(property\_address\_city file\_year)=3&                     &                     &                     & -21284383.9         \\
                    &                     &                     &                     &     (-1.85)         \\
\addlinespace
group(property\_address\_city file\_year)=7&                     &                     &                     & -38581122.2\sym{***}\\
                    &                     &                     &                     &     (-4.94)         \\
\addlinespace
group(property\_address\_city file\_year)=8&                     &                     &                     & -38411331.2\sym{***}\\
                    &                     &                     &                     &     (-4.90)         \\
\addlinespace
group(property\_address\_city file\_year)=9&                     &                     &                     & -34767371.4\sym{***}\\
                    &                     &                     &                     &     (-4.31)         \\
\addlinespace
group(property\_address\_city file\_year)=11&                     &                     &                     & -34630813.9\sym{***}\\
                    &                     &                     &                     &     (-4.27)         \\
\addlinespace
group(property\_address\_city file\_year)=12&                     &                     &                     & -26507586.7\sym{**} \\
                    &                     &                     &                     &     (-3.25)         \\
\addlinespace
group(property\_address\_city file\_year)=13&                     &                     &                     &  -7386286.8         \\
                    &                     &                     &                     &     (-0.72)         \\
\addlinespace
group(property\_address\_city file\_year)=14&                     &                     &                     & -17859840.8         \\
                    &                     &                     &                     &     (-1.64)         \\
\addlinespace
group(property\_address\_city file\_year)=23&                     &                     &                     & -38408518.6\sym{***}\\
                    &                     &                     &                     &     (-4.91)         \\
\addlinespace
group(property\_address\_city file\_year)=24&                     &                     &                     & -36264514.4\sym{***}\\
                    &                     &                     &                     &     (-4.60)         \\
\addlinespace
group(property\_address\_city file\_year)=26&                     &                     &                     & -38279509.7\sym{***}\\
                    &                     &                     &                     &     (-4.89)         \\
\addlinespace
group(property\_address\_city file\_year)=31&                     &                     &                     &  -6458709.7         \\
                    &                     &                     &                     &     (-0.48)         \\
\addlinespace
group(property\_address\_city file\_year)=33&                     &                     &                     & -37591120.1\sym{***}\\
                    &                     &                     &                     &     (-4.81)         \\
\addlinespace
group(property\_address\_city file\_year)=34&                     &                     &                     & -36376733.5\sym{***}\\
                    &                     &                     &                     &     (-4.63)         \\
\addlinespace
group(property\_address\_city file\_year)=35&                     &                     &                     &   6571579.9         \\
                    &                     &                     &                     &      (0.24)         \\
\addlinespace
group(property\_address\_city file\_year)=39&                     &                     &                     & -26410797.0\sym{**} \\
                    &                     &                     &                     &     (-3.22)         \\
\addlinespace
group(property\_address\_city file\_year)=40&                     &                     &                     & -30562560.8\sym{***}\\
                    &                     &                     &                     &     (-3.63)         \\
\addlinespace
group(property\_address\_city file\_year)=42&                     &                     &                     &     17743.6         \\
                    &                     &                     &                     &      (0.00)         \\
\addlinespace
group(property\_address\_city file\_year)=43&                     &                     &                     &  -7566228.0         \\
                    &                     &                     &                     &     (-0.73)         \\
\addlinespace
group(property\_address\_city file\_year)=53&                     &                     &                     &  23206974.1\sym{*}  \\
                    &                     &                     &                     &      (2.30)         \\
\addlinespace
group(property\_address\_city file\_year)=54&                     &                     &                     & -37332881.4\sym{***}\\
                    &                     &                     &                     &     (-4.76)         \\
\addlinespace
group(property\_address\_city file\_year)=56&                     &                     &                     &   -474304.1         \\
                    &                     &                     &                     &     (-0.05)         \\
\addlinespace
group(property\_address\_city file\_year)=58&                     &                     &                     & -33587109.7\sym{***}\\
                    &                     &                     &                     &     (-4.28)         \\
\addlinespace
group(property\_address\_city file\_year)=59&                     &                     &                     & -34174537.7\sym{***}\\
                    &                     &                     &                     &     (-4.34)         \\
\addlinespace
group(property\_address\_city file\_year)=60&                     &                     &                     & -26000080.5\sym{**} \\
                    &                     &                     &                     &     (-2.61)         \\
\addlinespace
group(property\_address\_city file\_year)=66&                     &                     &                     &  30346290.9         \\
                    &                     &                     &                     &      (1.64)         \\
\addlinespace
group(property\_address\_city file\_year)=67&                     &                     &                     &  -1766588.2         \\
                    &                     &                     &                     &     (-0.18)         \\
\addlinespace
group(property\_address\_city file\_year)=68&                     &                     &                     & -17027153.2         \\
                    &                     &                     &                     &     (-1.44)         \\
\addlinespace
group(property\_address\_city file\_year)=73&                     &                     &                     & -16144028.9\sym{*}  \\
                    &                     &                     &                     &     (-2.06)         \\
\addlinespace
group(property\_address\_city file\_year)=74&                     &                     &                     & -31298276.4\sym{***}\\
                    &                     &                     &                     &     (-3.53)         \\
\addlinespace
group(property\_address\_city file\_year)=75&                     &                     &                     &  -7340083.6         \\
                    &                     &                     &                     &     (-0.70)         \\
\addlinespace
group(property\_address\_city file\_year)=83&                     &                     &                     & -35489242.1\sym{***}\\
                    &                     &                     &                     &     (-4.50)         \\
\addlinespace
group(property\_address\_city file\_year)=84&                     &                     &                     & -37890557.6\sym{***}\\
                    &                     &                     &                     &     (-4.84)         \\
\addlinespace
group(property\_address\_city file\_year)=88&                     &                     &                     &  24176473.6         \\
                    &                     &                     &                     &      (1.77)         \\
\addlinespace
group(property\_address\_city file\_year)=92&                     &                     &                     & -12488676.4         \\
                    &                     &                     &                     &     (-1.06)         \\
\addlinespace
group(property\_address\_city file\_year)=99&                     &                     &                     & -35936941.8\sym{***}\\
                    &                     &                     &                     &     (-4.50)         \\
\addlinespace
group(property\_address\_city file\_year)=100&                     &                     &                     & -38696642.4\sym{***}\\
                    &                     &                     &                     &     (-4.94)         \\
\addlinespace
group(property\_address\_city file\_year)=103&                     &                     &                     & -28496105.0\sym{**} \\
                    &                     &                     &                     &     (-3.22)         \\
\addlinespace
group(property\_address\_city file\_year)=113&                     &                     &                     & -30890843.1\sym{***}\\
                    &                     &                     &                     &     (-3.52)         \\
\addlinespace
group(property\_address\_city file\_year)=120&                     &                     &                     & -20911443.0         \\
                    &                     &                     &                     &     (-1.95)         \\
\addlinespace
group(property\_address\_city file\_year)=121&                     &                     &                     & -38546947.5\sym{***}\\
                    &                     &                     &                     &     (-4.93)         \\
\addlinespace
group(property\_address\_city file\_year)=122&                     &                     &                     & -36566747.8\sym{***}\\
                    &                     &                     &                     &     (-4.61)         \\
\addlinespace
group(property\_address\_city file\_year)=123&                     &                     &                     & -33882902.8\sym{***}\\
                    &                     &                     &                     &     (-4.31)         \\
\addlinespace
group(property\_address\_city file\_year)=125&                     &                     &                     & -35520028.9\sym{***}\\
                    &                     &                     &                     &     (-4.50)         \\
\addlinespace
group(property\_address\_city file\_year)=126&                     &                     &                     & -34208737.4\sym{***}\\
                    &                     &                     &                     &     (-4.16)         \\
\addlinespace
group(property\_address\_city file\_year)=127&                     &                     &                     & -37615554.7\sym{***}\\
                    &                     &                     &                     &     (-4.81)         \\
\addlinespace
group(property\_address\_city file\_year)=128&                     &                     &                     & -37542381.2\sym{***}\\
                    &                     &                     &                     &     (-4.80)         \\
\addlinespace
group(property\_address\_city file\_year)=132&                     &                     &                     &  10784136.1         \\
                    &                     &                     &                     &      (1.37)         \\
\addlinespace
group(property\_address\_city file\_year)=134&                     &                     &                     &   9632586.1         \\
                    &                     &                     &                     &      (1.22)         \\
\addlinespace
group(property\_address\_city file\_year)=135&                     &                     &                     & -16437743.6\sym{*}  \\
                    &                     &                     &                     &     (-1.99)         \\
\addlinespace
group(property\_address\_city file\_year)=136&                     &                     &                     & -20864508.2\sym{*}  \\
                    &                     &                     &                     &     (-2.23)         \\
\addlinespace
group(property\_address\_city file\_year)=137&                     &                     &                     &  -7993710.8         \\
                    &                     &                     &                     &     (-0.74)         \\
\addlinespace
group(property\_address\_city file\_year)=138&                     &                     &                     & -34985127.9\sym{***}\\
                    &                     &                     &                     &     (-4.42)         \\
\addlinespace
group(property\_address\_city file\_year)=142&                     &                     &                     & -31556449.3\sym{***}\\
                    &                     &                     &                     &     (-3.94)         \\
\addlinespace
group(property\_address\_city file\_year)=143&                     &                     &                     & -28620927.6\sym{***}\\
                    &                     &                     &                     &     (-3.48)         \\
\addlinespace
group(property\_address\_city file\_year)=144&                     &                     &                     & -28153048.9\sym{**} \\
                    &                     &                     &                     &     (-3.16)         \\
\addlinespace
group(property\_address\_city file\_year)=147&                     &                     &                     & -35823404.4\sym{***}\\
                    &                     &                     &                     &     (-4.51)         \\
\addlinespace
group(property\_address\_city file\_year)=153&                     &                     &                     & -38485321.4\sym{***}\\
                    &                     &                     &                     &     (-4.92)         \\
\addlinespace
group(property\_address\_city file\_year)=156&                     &                     &                     & -33011555.7\sym{***}\\
                    &                     &                     &                     &     (-4.19)         \\
\addlinespace
group(property\_address\_city file\_year)=164&                     &                     &                     & -36537387.6\sym{***}\\
                    &                     &                     &                     &     (-4.65)         \\
\addlinespace
group(property\_address\_city file\_year)=167&                     &                     &                     & -38203020.1\sym{***}\\
                    &                     &                     &                     &     (-4.89)         \\
\addlinespace
group(property\_address\_city file\_year)=168&                     &                     &                     & -31817841.1\sym{***}\\
                    &                     &                     &                     &     (-3.55)         \\
\addlinespace
group(property\_address\_city file\_year)=169&                     &                     &                     & -25178303.5\sym{*}  \\
                    &                     &                     &                     &     (-2.30)         \\
\addlinespace
group(property\_address\_city file\_year)=171&                     &                     &                     & -36001309.4\sym{***}\\
                    &                     &                     &                     &     (-4.57)         \\
\addlinespace
group(property\_address\_city file\_year)=172&                     &                     &                     & -38116676.0\sym{***}\\
                    &                     &                     &                     &     (-4.88)         \\
\addlinespace
group(property\_address\_city file\_year)=173&                     &                     &                     & -37655672.3\sym{***}\\
                    &                     &                     &                     &     (-4.75)         \\
\addlinespace
group(property\_address\_city file\_year)=174&                     &                     &                     & -35945808.4\sym{***}\\
                    &                     &                     &                     &     (-4.55)         \\
\addlinespace
group(property\_address\_city file\_year)=179&                     &                     &                     & -35689685.3\sym{***}\\
                    &                     &                     &                     &     (-4.52)         \\
\addlinespace
group(property\_address\_city file\_year)=180&                     &                     &                     & -30243768.9\sym{***}\\
                    &                     &                     &                     &     (-3.70)         \\
\addlinespace
group(property\_address\_city file\_year)=182&                     &                     &                     & -35512860.3\sym{***}\\
                    &                     &                     &                     &     (-4.53)         \\
\addlinespace
group(property\_address\_city file\_year)=183&                     &                     &                     & -35437021.0\sym{***}\\
                    &                     &                     &                     &     (-4.52)         \\
\addlinespace
group(property\_address\_city file\_year)=187&                     &                     &                     & -33818835.1\sym{***}\\

>>>>

{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabular}{l*{4}{c}}
\toprule
                    &\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}\\
                    &        b/se&        b/se&        b/se&        b/se\\
\midrule
judgment\_for\_plaintiff& 3259177.986& 1507062.672& 1507062.672&  751962.414\\
                    & (762388.53)& (577088.19)& (577088.19)&(2866558.93)\\
\midrule
Observations        &        5567&        5567&        5567&        5567\\
\bottomrule
\end{tabular}
}
